---
title: "Trust and Partisan Segregation"
author: "Noah Daponte-Smith"
date: "4/22/2022"
output: pdf_document
---

```{r setup, include=FALSE, warning = FALSE}
library(tidyverse)
library(estimatr)
library(knitr)
library(modelsummary)
library(lfe)
setwd("C:/Users/dapon/Dropbox/Harvard/trust/data")
full <- read_csv("survey_clean/2021-recontact-with-seg-variables.csv")

```

\section{Bivariate correlations}
These are the bivariate correlations between the trust variables and the measures of partisan exposure. I report the correlations for the full sample and for subsets of Biden and Trump voters. 
```{r raw_correlations, message = FALSE, echo = FALSE, warning = FALSE}
full_cor <- full %>% 
  select(denisen_general, denisen_neighbor, pres_vote_2020,
         w.mean.d.post, w.mean.r.post) %>% 
  na.omit() 



general_demexp_cor <- cor(full_cor$denisen_general, full_cor$w.mean.d.post)
neighbor_demexp_cor <- cor(full_cor$denisen_neighbor, full_cor$w.mean.d.post)
general_repexp_cor <- cor(full_cor$denisen_general, full_cor$w.mean.r.post)
neighbor_repexp_cor <- cor(full_cor$denisen_neighbor, full_cor$w.mean.r.post)


general_demexp_cor_dem <- cor(full_cor$denisen_general[full_cor$pres_vote_2020 == "Joe Biden"],
                                full_cor$w.mean.d.post[full_cor$pres_vote_2020 == "Joe Biden"])
neighbor_demexp_cor_dem <- cor(full_cor$denisen_neighbor[full_cor$pres_vote_2020 == "Joe Biden"],
                                full_cor$w.mean.d.post[full_cor$pres_vote_2020 == "Joe Biden"])
general_repexp_cor_dem <- cor(full_cor$denisen_general[full_cor$pres_vote_2020 == "Joe Biden"],
                                full_cor$w.mean.r.post[full_cor$pres_vote_2020 == "Joe Biden"])
neighbor_repexp_cor_dem <- cor(full_cor$denisen_neighbor[full_cor$pres_vote_2020 == "Joe Biden"],
                                full_cor$w.mean.r.post[full_cor$pres_vote_2020 == "Joe Biden"])

general_demexp_cor_rep <- cor(full_cor$denisen_general[full_cor$pres_vote_2020 == "Donald Trump"],
                                full_cor$w.mean.d.post[full_cor$pres_vote_2020 == "Donald Trump"])
neighbor_demexp_cor_rep <- cor(full_cor$denisen_neighbor[full_cor$pres_vote_2020 == "Donald Trump"],
                                full_cor$w.mean.d.post[full_cor$pres_vote_2020 == "Donald Trump"])
general_repexp_cor_rep <- cor(full_cor$denisen_general[full_cor$pres_vote_2020 == "Donald Trump"],
                                full_cor$w.mean.r.post[full_cor$pres_vote_2020 == "Donald Trump"])
neighbor_repexp_cor_rep <- cor(full_cor$denisen_neighbor[full_cor$pres_vote_2020 == "Donald Trump"],
                                full_cor$w.mean.r.post[full_cor$pres_vote_2020 == "Donald Trump"])


cbind(c("General trust vs. Dem exposure",
        "Neighbor trust vs. Dem exposure",
        "General trust vs. Rep exposure",
        "Neighbor trust vs. Rep exposure",
        "General trust vs. Dem exposure",
        "Neighbor trust vs. Dem exposure",
        "General trust vs. Rep exposure",
        "Neighbor trust vs. Rep exposure",
        "General trust vs. Dem exposure",
        "Neighbor trust vs. Dem exposure",
        "General trust vs. Rep exposure",
        "Neighbor trust vs. Rep exposure"),
      c("Full","Full","Full","Full",
        "Dem","Dem","Dem","Dem",
        "Rep","Rep","Rep","Rep"),
   c(round(general_demexp_cor, 3),
     round(neighbor_demexp_cor, 3),
    round(general_repexp_cor, 3), 
    round(neighbor_repexp_cor, 3),
    round(general_demexp_cor_dem, 3),
    round(neighbor_demexp_cor_dem, 3),
    round(general_repexp_cor_dem, 3),
    round(neighbor_repexp_cor_dem, 3),
    round(general_demexp_cor_rep, 3),
    round(neighbor_demexp_cor_rep, 3 ),
    round(general_repexp_cor_rep, 3),
    round(neighbor_repexp_cor_rep, 3)
    )) %>% 
  as_tibble() %>% 
  rename(Relationship = V1, 
         Group = V2, 
         Coefficient = V3) %>% 
  kable()
      
```


\section{County fixed effects}

## General trust and trust in neighbors, by 2020 vote


```{r 2020vote, echo = FALSE, warning = FALSE, message = FALSE}
# get only trump and biden voters
df_twoparty <- full %>% 
    filter(pres_vote_2020 %in% c("Donald Trump","Joe Biden")) %>% 
    mutate(vote_biden = ifelse(pres_vote_2020 == "Joe Biden", 1, 0))
  
  # democratic exposure, general trust, pres vote choice 
mod_general_dem_pres_county <- lm_robust(data = df_twoparty, 
                                          denisen_general ~ w.mean.d.post*vote_biden + 
                                            gender + edlevel + white_non_hispanic + age + income_ordinal + 
                                          non_white_prop + poverty_rate + median_income,
                                          fixed_effects = vb.vf_county_code,
                                         clusters = vb.vf_county_code)
  # democratic exposure, neighbors trust, pres vote choice 
mod_neighbors_dem_pres_county <- lm_robust(
    data = df_twoparty, denisen_neighbor ~ 
      w.mean.d.post*vote_biden + 
      gender + edlevel + white_non_hispanic + age + income_ordinal + 
      non_white_prop + poverty_rate + median_income, 
    fixed_effects = vb.vf_county_code,
    clusters = vb.vf_county_code)

  # democratic exposure, general trust, pres vote choice 
mod_general_rep_pres_county <- lm_robust(data = df_twoparty, 
                                          denisen_general ~ w.mean.r.post*vote_biden + 
                                            gender + edlevel + white_non_hispanic + age + income_ordinal + 
                                          non_white_prop + poverty_rate + median_income,
                                          fixed_effects = vb.vf_county_code,
                                         clusters = vb.vf_county_code)
  # democratic exposure, neighbors trust, pres vote choice 
mod_neighbors_rep_pres_county <- lm_robust(
    data = df_twoparty, denisen_neighbor ~ 
      w.mean.r.post*vote_biden + 
      gender + edlevel + white_non_hispanic + age + income_ordinal + 
      non_white_prop + poverty_rate + median_income, 
    fixed_effects = vb.vf_county_code,
    clusters = vb.vf_county_code)


# report the pres-vote results 
modelsummary(
    list("General trust, Dem exposure" = mod_general_dem_pres_county, 
         "Neighbors trust, Dem exposure" = mod_neighbors_dem_pres_county,
         "General trust, Rep exposure" = mod_general_rep_pres_county,
         "Neighbors trust, Rep exposure" = mod_neighbors_rep_pres_county),
    output = "markdown",
    stars = TRUE,
    coef_map = c(
      "w.mean.d.post" = "Dem exposure (weighted)", 
      "vote_biden" = "Voted Biden",
      "w.mean.d.post:vote_biden" = "Dem exposure * Voted Biden",
      "w.mean.r.post" = "Rep exposure (weighted)",
      "w.mean.r.post:vote_biden" = "Rep exposure * Voted Biden",
      "genderMale" = "Gender Male",
      "genderOther/Prefer not to answer" = "Gender Other",
      "edlevel" = "Education (ordinal)",
      "white_non_hispanic" = "White (non-Hispanic)",
      "age" = "Age",
      "income_ordinal" = "Income (ordinal)",
      "non_white_prop" = "Pct. non-white (blockgroup)",
      "poverty_rate" = "Poverty rate (blockgroup)",
      "median_income" = "Median income (blockgroup)"
      
    ),
    add_rows = bind_rows(bind_cols("County fixed effects","Yes","Yes", "Yes","Yes"),
                      bind_cols("Std. Error Clusters","County","County","County","County")),
    title = "General/neighbors trust, by presidential vote and partisan exposure",
  )

```

\newpage

## General trust and trust in neighbors, by  party-id (among Dem and Rep partisans)
```{r two_party_id, echo = FALSE, warning = FALSE, message = FALSE}
# democratic exposure, general trust, two-party id 
mod_general_dem_partyid_county <- lm_robust(
  data = full, 
  denisen_general ~ w.mean.d.post*democrat_id_twoparty + 
    gender + edlevel + white_non_hispanic + age + income_ordinal + 
    non_white_prop + poverty_rate + median_income, 
  fixed_effects = vb.vf_county_code, 
  clusters = vb.vf_county_code
)
# democratic exposure, neighbors trust, two-party id 
mod_neighbors_dem_partyid_county <- lm_robust(
  data = full, 
  denisen_neighbor ~ w.mean.d.post*democrat_id_twoparty + 
    gender + edlevel + white_non_hispanic + age + income_ordinal + 
    non_white_prop + poverty_rate + median_income, 
  fixed_effects = vb.vf_county_code, 
  clusters = vb.vf_county_code
)

# democratic exposure, general trust, two-party id 
mod_general_rep_partyid_county <- lm_robust(
  data = full, 
  denisen_general ~ w.mean.r.post*democrat_id_twoparty + 
    gender + edlevel + white_non_hispanic + age + income_ordinal + 
    non_white_prop + poverty_rate + median_income, 
  fixed_effects = vb.vf_county_code, 
  clusters = vb.vf_county_code
)
# democratic exposure, neighbors trust, two-party id 
mod_neighbors_rep_partyid_county <- lm_robust(
  data = full, 
  denisen_neighbor ~ w.mean.r.post*democrat_id_twoparty + 
    gender + edlevel + white_non_hispanic + age + income_ordinal + 
    non_white_prop + poverty_rate + median_income, 
  fixed_effects = vb.vf_county_code, 
  clusters = vb.vf_county_code
)

modelsummary(
  list("General trust, Dem exposure" = mod_general_dem_partyid_county, 
       "Neighbors trust, Dem exposure" = mod_neighbors_dem_partyid_county,
       "General trust, Rep exposure" = mod_general_rep_partyid_county,
       "Neighbors trust, Rep exposure" = mod_neighbors_rep_partyid_county), 
  stars = TRUE,
  output = "markdown",
  coef_map = c("w.mean.d.post" = "Dem exposure (weighted)",
               "democrat_id_twoparty" = "Party ID = Dem", 
               "w.mean.d.post:democrat_id_twoparty" = "Dem exposure * Party ID = Dem", 
               "w.mean.r.post" = "Rep exposure (weighted)",
               "w.mean.r.post:democrat_id_twoparty" = "Rep exposure * Party ID = Dem",
               "genderMale" = "Gender Male",
               "genderOther/Prefer not to answer" = "Gender Other",
               "edlevel" = "Education (ordinal)",
               "white_non_hispanic" = "White (non-Hispanic)",
               "age" = "Age",
               "income_ordinal" = "Income (ordinal)",
               "non_white_prop" = "Pct. non-white (blockgroup)",
               "poverty_rate" = "Poverty rate (blockgroup)",
               "median_income" = "Median income (blockgroup)"),
  add_rows = bind_rows(bind_cols("County fixed effects","Yes","Yes", "Yes","Yes"),
                       bind_cols("Std. Error Clusters","County","County","County","County")),
  title = "General/neighbors trust, by two-party ID and partisan exposure",
)


```




\newpage
## General trust and trust in neighbors, by party ID (Rep, Dem, Ind)
```{r three_party_id, echo = FALSE, warning = FALSE, message = FALSE}
threeparty_dat <- full %>% filter(party_3 %in% c("Democrat","Republican","Independent")) %>% 
    mutate(party_5_factor = factor(party_3, levels = c("Republican","Democrat","Independent")))
# democratic exposure, general trust, party id (with independents)
mod_general_dem_threepartyid_county <- lm_robust(
  data =  threeparty_dat, 
  denisen_general ~ w.mean.d.post*party_3_factor + 
    gender + edlevel + white_non_hispanic + age + income_ordinal + 
    non_white_prop + poverty_rate + median_income, 
  fixed_effects = vb.vf_county_code, 
  clusters = vb.vf_county_code
)
# democratic exposure, neighbors trust, party id (with independents)
mod_neighbors_dem_threepartyid_county <- lm_robust( 
  data = threeparty_dat, 
  denisen_neighbor ~ w.mean.d.post*party_3_factor + 
    gender + edlevel + white_non_hispanic + age + income_ordinal + 
    non_white_prop + poverty_rate + median_income, 
  fixed_effects = vb.vf_county_code, 
  clusters = vb.vf_county_code
)
  
# report the party id  results 
modelsummary(
  list("General trust" = mod_general_dem_threepartyid_county, 
       "Neighbors trust" = mod_neighbors_dem_threepartyid_county),
  stars = TRUE,
  output = "markdown",
  coef_map = c("w.mean.d.post" = "Democratic exposure (weighted)",
               "party_3_factorIndependent" = "Party ID = Independent",
               "party_3_factorRepublican" = "Party ID = Rep",
               "w.mean.d.post:party_3_factorRepublican" = "Dem exposure * Party ID = Rep",
               "w.mean.d.post:party_3_factorIndependent" = "Dem exposure * Party ID = Ind",
               "genderMale" = "Gender Male",
               "genderOther/Prefer not to answer" = "Gender Other",
               "edlevel" = "Education (ordinal)",
               "white_non_hispanic" = "White (non-Hispanic)",
               "age" = "Age",
               "income_ordinal" = "Income (ordinal)",
               "non_white_prop" = "Pct. non-white (blockgroup)",
               "poverty_rate" = "Poverty rate (blockgroup)",
               "median_income" = "Median income (blockgroup)"),
  add_rows = bind_rows(bind_cols("County fixed effects","Yes","Yes"),
                       bind_cols("Std. Error Clusters","County","County")),
  title = "General/neighbors trust, by three-party ID and partisan exposure",
)

```




\newpage 

\section{Zip code fixed effects}

I now replicate the above models, but make the fixed effects more punishing: Zip codes rather than counties. The significance mostly disappears with this set of fixed effects. 

## General/neighbors trust, by  2020 vote (zip code FEs)
```{r zip_fes, echo = FALSE, warning = FALSE, message = FALSE}

# get only trump and biden voters
df_twoparty <- full %>% 
    filter(pres_vote_2020 %in% c("Donald Trump","Joe Biden")) %>% 
    mutate(vote_biden = ifelse(pres_vote_2020 == "Joe Biden", 1, 0))
  
  # democratic exposure, general trust, pres vote choice 
mod_general_dem_pres_zip <- felm(data = df_twoparty, 
                                          denisen_general ~ w.mean.d.post*vote_biden + 
                                            gender + edlevel + white_non_hispanic + age + income_ordinal + 
                                          non_white_prop + poverty_rate + median_income | 
                                      vb.tsmart_zip | 0 | vb.tsmart_zip)

  # democratic exposure, neighbors trust, pres vote choice 
mod_neighbors_dem_pres_zip <- felm(data = df_twoparty, 
                                          denisen_neighbor ~ w.mean.d.post*vote_biden + 
                                            gender + edlevel + white_non_hispanic + age + income_ordinal + 
                                          non_white_prop + poverty_rate + median_income | 
                                      vb.tsmart_zip | 0 | vb.tsmart_zip)

  # republican exposure, general trust, pres vote choice 
mod_general_rep_pres_zip <- felm(data = df_twoparty, 
                                          denisen_general ~ w.mean.r.post*vote_biden + 
                                            gender + edlevel + white_non_hispanic + age + income_ordinal + 
                                          non_white_prop + poverty_rate + median_income | 
                                      vb.tsmart_zip | 0 | vb.tsmart_zip)

  # republican exposure, neighbors trust, pres vote choice 
mod_neighbors_rep_pres_zip <- felm(data = df_twoparty, 
                                          denisen_neighbor ~ w.mean.r.post*vote_biden + 
                                            gender + edlevel + white_non_hispanic + age + income_ordinal + 
                                          non_white_prop + poverty_rate + median_income | 
                                      vb.tsmart_zip | 0 | vb.tsmart_zip)




# report the pres-vote results 
modelsummary(
    list("General trust, Dem exposure" = mod_general_dem_pres_zip, 
         "Neighbors trust, Dem exposure" = mod_neighbors_dem_pres_zip,
         "General trust, Rep exposure" = mod_general_rep_pres_zip,
         "Neighbors trust, Rep exposure" = mod_neighbors_rep_pres_zip),
    output = "markdown",
    stars = TRUE,
    coef_map = c(
      "w.mean.d.post" = "Dem exposure (weighted)", 
      "vote_biden" = "Voted Biden",
      "w.mean.d.post:vote_biden" = "Dem exposure * Voted Biden",
      "w.mean.r.post" = "Rep exposure (weighted)",
      "w.mean.r.post:vote_biden" = "Rep exposure * Voted Biden",
      "genderMale" = "Gender Male",
      "genderOther/Prefer not to answer" = "Gender Other",
      "edlevel" = "Education (ordinal)",
      "white_non_hispanic" = "White (non-Hispanic)",
      "age" = "Age",
      "income_ordinal" = "Income (ordinal)",
      "non_white_prop" = "Pct. non-white (blockgroup)",
      "poverty_rate" = "Poverty rate (blockgroup)",
      "median_income" = "Median income (blockgroup)"
      
    ),
    add_rows = bind_rows(bind_cols("ZIP fixed effects","Yes","Yes", "Yes","Yes"),
                      bind_cols("Std. Error Clusters","ZIP","ZIP","ZIP","ZIP")),
    title = "General/neighbors trust, by presidential vote and partisan exposure",
  )
```
\newpage

## General/neighbors trust, by  two-party ID (zip code FEs)


```{r zip_fes_twoparty_id, echo = FALSE, warning = FALSE, message = FALSE}

  # democratic exposure, general trust, pres vote choice 
mod_general_dem_partyid_zip <- felm(data = df_twoparty, 
                                          denisen_general ~ w.mean.d.post*democrat_id_twoparty + 
                                            gender + edlevel + white_non_hispanic + age + income_ordinal + 
                                          non_white_prop + poverty_rate + median_income | 
                                      vb.tsmart_zip | 0 | vb.tsmart_zip)

  # democratic exposure, neighbors trust, pres vote choice 
mod_neighbors_dem_partyid_zip <- felm(data = df_twoparty, 
                                          denisen_neighbor ~ w.mean.d.post*democrat_id_twoparty + 
                                            gender + edlevel + white_non_hispanic + age + income_ordinal + 
                                          non_white_prop + poverty_rate + median_income | 
                                      vb.tsmart_zip | 0 | vb.tsmart_zip)

  # republican exposure, general trust, pres vote choice 
mod_general_rep_partyid_zip <- felm(data = df_twoparty, 
                                          denisen_general ~ w.mean.r.post*democrat_id_twoparty + 
                                            gender + edlevel + white_non_hispanic + age + income_ordinal + 
                                          non_white_prop + poverty_rate + median_income | 
                                      vb.tsmart_zip | 0 | vb.tsmart_zip)

  # republican exposure, neighbors trust, pres vote choice 
mod_neighbors_rep_partyid_zip <- felm(data = df_twoparty, 
                                          denisen_neighbor ~ w.mean.r.post*democrat_id_twoparty + 
                                            gender + edlevel + white_non_hispanic + age + income_ordinal + 
                                          non_white_prop + poverty_rate + median_income | 
                                      vb.tsmart_zip | 0 | vb.tsmart_zip)

modelsummary(
  list("General trust, Dem exposure" = mod_general_dem_partyid_zip, 
       "Neighbors trust, Dem exposure" = mod_neighbors_dem_partyid_zip,
       "General trust, Rep exposure" = mod_general_rep_partyid_zip,
       "Neighbors trust, Rep exposure" = mod_neighbors_rep_partyid_zip), 
  stars = TRUE,
  output = "markdown",
  coef_map = c("w.mean.d.post" = "Dem exposure (weighted)",
               "democrat_id_twoparty" = "Party ID = Dem", 
               "w.mean.d.post:democrat_id_twoparty" = "Dem exposure * Party ID = Dem", 
               "w.mean.r.post" = "Rep exposure (weighted)",
               "w.mean.r.post:democrat_id_twoparty" = "Rep exposure * Party ID = Dem",
               "genderMale" = "Gender Male",
               "genderOther/Prefer not to answer" = "Gender Other",
               "edlevel" = "Education (ordinal)",
               "white_non_hispanic" = "White (non-Hispanic)",
               "age" = "Age",
               "income_ordinal" = "Income (ordinal)",
               "non_white_prop" = "Pct. non-white (blockgroup)",
               "poverty_rate" = "Poverty rate (blockgroup)",
               "median_income" = "Median income (blockgroup)"),
  add_rows = bind_rows(bind_cols("Zip fixed effects","Yes","Yes", "Yes","Yes"),
                       bind_cols("Std. Error Clusters","Zip","Zip","Zip","Zip")),
  title = "General/neighbors trust, by two-party ID and partisan exposure",
)



```
\newpage
## General/neighbors trust, by  threes-party ID (zip code FEs)

```{r zip_fes_threeparty, echo = FALSE, warning = FALSE, message = FALSE}
threeparty_dat <-  full %>% filter(party_3 %in% c("Democrat","Republican","Independent")) %>% 
    mutate(party_3_factor = factor(party_3, levels = c("Republican","Democrat","Independent"))) 

  # democratic exposure, general trust, pres vote choice 
mod_general_dem_threeparty_zip <- felm(data = threeparty_dat, 
                                          denisen_general ~ w.mean.d.post*party_3_factor + 
                                            gender + edlevel + white_non_hispanic + age + income_ordinal + 
                                          non_white_prop + poverty_rate + median_income | 
                                      vb.tsmart_zip | 0 | vb.tsmart_zip)

  # democratic exposure, neighbors trust, pres vote choice 
mod_neighbors_dem_threeparty_zip <- felm(data = threeparty_dat, 
                                          denisen_neighbor ~ w.mean.d.post*party_3_factor + 
                                            gender + edlevel + white_non_hispanic + age + income_ordinal + 
                                          non_white_prop + poverty_rate + median_income | 
                                      vb.tsmart_zip | 0 | vb.tsmart_zip)

  # republican exposure, general trust, pres vote choice 
mod_general_rep_threeparty_zip <- felm(data = threeparty_dat, 
                                          denisen_general ~ w.mean.r.post*party_3_factor + 
                                            gender + edlevel + white_non_hispanic + age + income_ordinal + 
                                          non_white_prop + poverty_rate + median_income | 
                                      vb.tsmart_zip | 0 | vb.tsmart_zip)

  # republican exposure, neighbors trust, pres vote choice 
mod_neighbors_rep_threeparty_zip <- felm(data = threeparty_dat, 
                                          denisen_neighbor ~ w.mean.r.post*party_3_factor + 
                                            gender + edlevel + white_non_hispanic + age + income_ordinal + 
                                          non_white_prop + poverty_rate + median_income | 
                                      vb.tsmart_zip | 0 | vb.tsmart_zip)





# report the party id  results 
modelsummary(
    list("General trust, Dem exposure" = mod_general_dem_threeparty_zip, 
       "Neighbors trust, Dem exposure" = mod_neighbors_dem_threeparty_zip,
       "General trust, Rep exposure" = mod_general_rep_threeparty_zip,
       "Neighbors trust, Rep exposure" = mod_neighbors_rep_threeparty_zip), 
  stars = TRUE,
  output = "markdown",
  coef_map = c("w.mean.d.post" = "Democratic exposure (weighted)",
               "party_3_factorIndependent" = "Party ID = Independent",
               "party_3_factorRepublican" = "Party ID = Democrat",
               "w.mean.d.post:party_3_factorRepublican" = "Dem exposure * Party ID = Rep",
               "w.mean.d.post:party_3_factorIndependent" = "Dem exposure * Party ID = Ind",
               "w.mean.r.post:party_3_factorRepublican" = "Rep exposure * Party ID = Rep",
               "w.mean.r.post:party_3_factorIndependent" = "Rep exposure * Party ID = Ind",
               "genderMale" = "Gender Male",
               "genderOther/Prefer not to answer" = "Gender Other",
               "edlevel" = "Education (ordinal)",
               "white_non_hispanic" = "White (non-Hispanic)",
               "age" = "Age",
               "income_ordinal" = "Income (ordinal)",
               "non_white_prop" = "Pct. non-white (blockgroup)",
               "poverty_rate" = "Poverty rate (blockgroup)",
               "median_income" = "Median income (blockgroup)"),
  add_rows = bind_rows(bind_cols("Zip fixed effects","Yes","Yes","Yes","Yes"),
                       bind_cols("Std. Error Clusters","Zip","Zip","Zip","Zip")),
  title = "General/neighbors trust, by three-party ID and partisan exposure",
)

```


